\documentclass[ebook,12pt,twoside,openright,extrafontsizes,final]{memoir}
\usepackage{fontspec}
\usepackage{lettrine}
\usepackage[autocompile]{gregoriotex}
\usepackage{multicol}
\setsecnumdepth{part} % Only number the parts.

\directlua{dofile("lua-functions.lua")}

%
% Gregorio Settings
%
%\definecolor{gregoriocolor}{RGB}{99,00,00}
\gresetlinecolor{gregoriocolor}
\gresetgregoriofont[op]{greciliae}
\grechangestyle{firstsyllableinitial}{\scshape}
\gresetlyriccentering{syllable}
\gresetannotationby{bottomline}
\gresetannotationvalign{top}

%
% Setup gregorio chant headers
%
\newcommand{\chantoccasion}{}
\newcommand{\chantauthor}{}
\newcommand{\chantdate}{}
\newcommand{\chanttranslator}{}
\newcommand{\chantincipit}{}
\newcommand{\captureoccasion}[1]{\renewcommand{\chantoccasion}{\expandafter#1}}
\newcommand{\captureauthor}[1]{\renewcommand{\chantauthor}{\expandafter#1}}
\newcommand{\capturdate}[1]{\renewcommand{\chantdate}{\expandafter#1}}
\newcommand{\capturetranslator}[1]{\renewcommand{\chanttranslator}{\expandafter#1}}
\newcommand{\capturename}[1]{\renewcommand{\chantincipit}{\expandafter#1}}

\gresetheadercapture{office}{captureoccasion}{string}
\gresetheadercapture{author}{captureauthor}{string}
\gresetheadercapture{date}{capturdate}{string}
\gresetheadercapture{translator}{capturetranslator}{string}
\gresetheadercapture{name}{capturename}{string}
\greafterheaders{
    \directlua{printheaders("\luatexluaescapestring{\chantoccasion}", "\luatexluaescapestring{\chantauthor}", "\luatexluaescapestring{\chantdate}", "\luatexluaescapestring{\chanttranslator}", "\luatexluaescapestring{\chantincipit}")}
    \captureoccasion{}
    \captureauthor{}
    \capturename{}
    \capturdate{}
    \capturetranslator{}
}

\setmainfont{EBGaramond}

\newcommand \red{\addfontfeature{Color=990000}}
\newcommand \R{{\red℟.\ }}
\newcommand \V{{\red℣.\ }}
\newcommand \etc{\emph{\red\&c.}}
\newcommand \minorheading[2]{{\unexpanded\expandafter{\scshape #1}} {\unexpanded\expandafter{\itshape #2}}}

% Path to chant directory, in case they should be moved out.
\newcommand*{\MyPath}{chants}

% Command to style hymns
% *Number*
% [[Office Hymn.]] Mattins           {C. 10th cent.  Tr. P. D}
%                Annue Christe, saeculorum Domine
\def\hymn#1{\gregorioscore{\MyPath/hymns/#1}\obeylines\hymna}
\def\hymnverses{\obeylines\hymna}
\newcommand{\hymna}[1]{
    \directlua{printhymn([[#1]])}
}

\medievalpage
\checkandfixthelayout

\begin{document}
\frontmatter
\title{Hymnale}
\author{Michael Shirk}
\date{MMXIX}
\maketitle



\mainmatter
\part{Service Music}
\chapter{Mattins \& Evensong}

\section{The Invitatory Psalm}

TODO:
Invitatory Anthems w/ Psalm Tone

\subsection{Tone III}
\gregorioscore{\MyPath/invitatories/veniteExultemusDomino3}

\subsection{Tone IV}
\emph{The blank notes must be omitted when the Psalm is sung without an Invitatory Anthem.}

\gregorioscore{\MyPath/invitatories/veniteExultemusDomino4}

\subsection{Tone VI}
\gregorioscore{\MyPath/invitatories/veniteExultemusDomino6}

\subsection{Tone VII}
\gregorioscore{\MyPath/invitatories/veniteExultemusDomino7}

\section{Pascha Nostrum}
TODO


\section{The Hymn of SS.\ Ambrose \& Austin}
\gregorioscore{\MyPath/canticles/te-deum}

simple tone omitted?

\section{Benectus es}
TODO

\section{Benecite?}
TODO

\section{The Song of Zachary}
\gregorioscore{\MyPath/canticles/benedictus-peregrin}

TODO Psalm Tone

\section{The Song of the Blessed Virgin Mary}
\gregorioscore{\MyPath/canticles/magnificat-peregrin}

TODO Psalm Tone

TODO Nunc Dimittis


\part{Hymns}
\chapter{Proper of the Season}
\section{Advent}
TODO

\section{Christmas}
TODO

\section{S.\ Stephen, Protomartyr}
TODO

\section{S.\ John, Ap.\ Ev.}
TODO

\section{The Holy Innocents}
TODO

\section{S.\ Thomas of Canterbury, M.}
TODO

\section{S.\ Sylvester, B.C.}
TODO

\section{The Circumcision of our Lord}
TODO

\section{Epiphany}
TODO

\section{From the Octave of the Epiphany till the First Sunday in Lent}
\subsection{Saturday}
\subsection{Sunday}
\subsection{Monday}
\subsection{Tuesday}
\subsection{Wednesday}
\subsection{Thursday}
\subsection{Friday}
\subsection{Saturday}

\section{The First Sunday in Lent and daily until the Third Sunday}

TODO

\section{The Third Sunday in Lent and daily until Passion Sunday}
TODO

\section{Passion Sunday and daily until Wednesday in Holy Week inclusive}
TODO

...

\section{Low Sunday}
TODO

\section{Ascension Day and daily until Whitsun Day}
TODO

\section{Whitsun Day}
TODO

\section{Trinity Sunday}
and daily until Corpus Christi
\hymn{adestoSanctaTrinitas}{
2 Thee all the armies of the sky
Adore, and laud, and magnify:
While Nature, in her triple frame,
For ever sanctifies thy Name.

3 And we, too, thanks and homage pay,
Thine own adoring flock to-day:
O join to that celestial song
The praises of our suppliant throng!

4 Light, sole and one, we thee confess,
With triple praise we rightly bless:
And Alpha and Omega own,
With every spirit round thy throne.

5 To thee, O Unbegotten One,
And thee, O Sole-begotten Son,
And thee, O Holy Ghost, we raise
Our equal and eternal praise.  Amen.
}

At Evensong.
\V Let us bless the Father, the Son, and the Holy Ghost.  \R Let us praise him, and magnify him for ever.

At Mattins.
\V Blessed art thou, O Lord, in the firmament of heaven.  \R And worthy to be praised and glorified for ever.

At Lauds
\hymn{oPaterSancte}{
2 Trinity holy! Unity unchanging!
Godhead essential! Goodness all unbounded!
Light of the Angels! Refuge of the friendless!
    Hope universal!

3 Duly its service giveth every creature;
All thy creation, Lord, in thee rejoiceth:
We too will hymn thee with our heart’s devotion;
    Graciously hear us.

4 Mightiest Godhead, unto thee be glory,
Trinal yet Onely, Infinite and Highest:
Glory and honour, song and praise beseem thee
    Now and for ever. Amen.
}
\V Blessed be the name of the Lord.  \R From this time forth for evermore.

\gregorioscore{\MyPath/processions/voceJubilantes}

\section{Corpus Christi}
and daily during the Octave

\hymn{sacrisSolemniis}{
2 Remember we that night,
When, the last Supper spread,
Christ, as we all believe,
The lamb, with leavenless bread,
Amongst his brethren shared,
And thus the Law obey’d,
Of old unto their sires declared.

3 The typick lamb consumed,
The Paschal feast complete,
The Lord unto the Twelve
His Body gave to eat;
The whole to all, no less
The whole to each, did mete
With his own hands, as we confess.

4 He gave them, weak and frail,
His Flesh, their food to be;
On them, downcast and sad,
His Blood bestowèd he:
And thus to them he spake,
‘Receive this Cup from me,
And all of you of this partake’.

5 When he this Sacrifice
To institute did will,
He to his Priests alone
That office to fulfil,
On this wise did confide—
To whom pertaineth still,
To take, and to the rest divide.

6 Lo! Angels’ Bread is made
The Bread of men to-day:
The living Bread from heav’n
With figures doth away:
O wondrous boon indeed!
Though poor and lowly, may
The servant on his Master feed.

7 Thee therefore we implore,
O Godhead, One in Three,
So may’st thou visit us
As we now worship thee;
And lead us on thy way,
That we at last may see
The Light wherein thou dwellest aye. Amen.
}
\V Thou didst give them bread from heaven.  \R Containing in itself all sweetness.

\hymn{pangeLinguaGloriosi}{
2 Given for us, for us descending
Of a Virgin to proceed,
Man with man in converse blending,
Scatter’d he the Gospel seed;
Till his sojourn drew to ending.
Which he closed in wondrous deed.

3 At the last great Supper seated,
Circled by his brethren’s band,
All the Law required, completed
In the feast its statutes planned,
To the Twelve himself he meted,
For their food, with his own hand.

4 Word made Flesh, by Word he maketh
Very bread his Flesh to be;
Man in wine Christ’s Blood partaketh,
And if senses fail to see,
Faith alone the true heart waketh
To behold the mystery.

5 Therefore we, before It bending,
This great Sacrament adore:
Types and shadows have their ending
In the new Rite evermore:
Faith, our outward sense amending,
Maketh good defects before.

6 Honour, laud, and praise addressing
To the Father and the Son,
Might ascribe we, virtue, blessing,
And eternal benison;
Holy Ghost, from Both progressing,
Equal laud to thee be done. Amen.
}
\V Thou didst give them bread from heaven.  \R Containing in itself all sweetness.

\hymn{verbumSupernumProdiens}{
2 By false disciple to be given
To foemen for his Blood athirst,
Himself, the living Bread from heav’n,
He gave to his disciples first.

3 To them he gave, in two-fold kind,
His very Flesh, his very Blood:
Of two-fold substance man is made.
And he of man would be the Food.

4 At birth our Brother he became,
Our Food, while seated at the board:
He died our Ransomer to be,
He reigns to be our great Reward.

5 O Saving Victim, opening wide
The gate of heav’n to man below:
Our foes press on from every side,
Thine aid supply, thy strength bestow.

6 To thy great Name be endless praise,
Immortal Godhead, One in Three!
O grant us endless length of days
In our true native land, with thee. Amen.
}
\V He maketh peace in thy borders.  \R And filleth thee with the flour of wheat.


\gregorioscore{\MyPath/processions/salveFestaCorpusChristi}
\hymnverses{
3 Here is the Body of Christ, that saveth from death everlasting,—
Food by the manna foretold, writ in the records of yore.

4 Here is the Father’s Word, of heaven and earth the Creator;
He, with the Father one, blest with his Godhead the world.

5 Here is the Angels’ Bread, to the righteous the food of salvation,—
Bread that availeth not them that receive it in sin.

6 He, the Incarnate God, who stablish’d the work of creation,
Trampling on hell’s dread hosts, ruleth, Redeemer and King.

7 He in the fulness of time was born by a wondrous conception,
Son of a spotless Maid, guest of a virginal womb.

8 His very Flesh and Blood he took, when at supper reclining,
And the disciples twelve fed with the mystical gifts.

9 Thus doth the Virgin-born, the Father’s infinite Wisdom,
Plead as a Victim true, laid on the altar of God.

10 Thron’d on the Cross in the flesh, o’er death he triumph’d in dying,
Saving the world from sin, cleans’d by the Water and Blood.

11 Purchasing life by death, his palms our Ransom extended;
And, when the third day dawn’d, rose in the flesh from the grave.

12 Grant us eternal rest, primeval Fountain of blessings;
Ours be the land where day dureth, and night is unknown.
}


\gregorioscore{\MyPath/processions/laudaSyonSalvatorem}

Amen, alleluya?


\section{From the Octave of Corpus Christi}
till the First Sunday in Advent
(Or, From Trinity Sunday to Advent/Trinity to Advent)
\subsection{Saturday}
Evensong
\hymn{oLuxBeataTrinitas}{
2 To thee our morning song of praise,
To thee our evening prayer we raise;
Thy glory suppliant we adore
For ever and for evermore.

3 All laud to God the Father be,
All praise, eternal Son, to thee,
All glory, as is ever meet,
To God the holy Paraclete. Amen.
}
\V Let our evening prayer come up before thee, O Lórd.  \R And let thy mercy descend upon ús.

\subsection{Sunday}
And through the week.

\hymn{nocteSurgentes}{
2 So may our Monarch pitifully hear us,
That we may merit with his Saints to enter
Mansions eternal, therewithal possessing
Joy beatific.

3 This he vouchsafe us, God for ever blessed,
Father eternal, Son, and Holy Spirit,
Whose is the glory, which through all creation
Ever resoundeth. Amen.
}
\V The Lord is high above all péople.  \R And his glory above the héavens.
TODO - weekday verse!


\hymn{ecceJamNoctis}{
2 So shall our Maker, of his great compassion,
Banish all sickness, kindly health bestowing;
And may he grant us, of a Father’s goodness,
Mansions in heaven.

3 This he vouchsafe us, God for ever blessed,
Father eternal, Son, and holy Spirit,
Whose is the glory, which through all creation
Ever resoundeth. Amen.
}
\V The Lord is Kíng.  \R He hath put on glorious apparel, allelúya.
TODO - weekday verse!


Hymn 13 (E)
TODO

\section{Dedication of a Church}
TODO


\chapter{Common of Saints}
\section{Of one or more Apostles or an Evangelist out of Eastertide}
\hymn{annueChriste}{
¶ Here let the special verse proper to the Feast be sung.
3 Save, O Redeemer, this thy noble handiwork,
Seal’d with the holy radiance of thy countenance:
Let no foul spirit rend by fraud or subtilty
Them for whose ransom thou hast paid death’s penalty.

4 Pity thy servants, pining in captivity,
Absolve the guilty, raise the fetter’d prisoners:
And thy redeemed ones, whom thy blood hath purchased,
Grant, King of goodness, joy with thee in Paradise.

5 To thee, O Jesu, Blessed Lord, for evermore
Be glory, virtue, honour and supremacy:
One with the Father, and the Holy Paraclete,
With whom thou reignest God from all eternity.  Amen.
}

\V Their sound is gone out into all lands.  \R And their words into the ends of the world.


\subsubsection{Special Verses}

\hymnverses{
\minorheading{S.\ Andrew.}{Andrea pie}
May Andrew, gentlest of the saintly company,
Implore forgiveness for our grievous trespasses;
That we, sore burden’d by offences manifold,
At his petition may obtain deliverance.

\minorheading{S.\ Thomas.}{O Thoma Christi}
May he, who, doubting, probed the Saviour’s pierced side,
Plead—thro’ the merits of those wounds adorable,
Whose streams atoning cleans’d the world’s iniquity,—
That all the foulness of our guilt be purified.

\minorheading{S.\ John.}{Bina celestis}
Twin lamps, adorning Heaven’s eternal palaces!
James, with thy brother John, divine Evangelist!
Entreat that pardon for his lowly suppliants,
Which Christ hath freely promised to the penitent.

\minorheading{Conversion of S.\ Paul.}{Doctor egregie}
O by thy doctrine, Paul, thou sage illustrious,
Guide us in virtue, raise our spirits heavenwards;
Till perfect knowledge stream on us abundantly,
And that which only is in part be done away.

\minorheading{S.\ Matthias.}{Matthia juste}
May just Matthias, who by lot was numbered
With thine Apostles, sharer of their dignity,
By his petitions loose the bands of wickedness,
That we inherit light and joy eternally.

\minorheading{S.\ James.}{Bina celestis}
(as above on the Feast of S. John.)

\minorheading{S.\ Peter’s chains.}{Jam bone pastor}
Peter, good shepherd, may thy ceaseless orisons,
For us prevailing, break the bands of wickedness:
For thou of old time didst receive authority
The gates to open, or to close, of Paradise.

\minorheading{S.\ Bartholomew.}{Bartolomee celi}
May thy petitions, golden star, Bartholomew,
Whose light the sunbeams far exceeds in brilliancy,
Raise souls beclouded to celestial purity,
And heal the sickness of our guilty consciences.

\minorheading{S.\ Matthew.}{Matthee sancte}
May saintly Matthew, high in twofold dignity,
To thee, O Jesu, plead with prayer importunate:
So ’mid life’s tempests may thy guidance succour us,
Lest death hereafter whelm us everlastingly.

\minorheading{SS.\ Simon \& Jude.}{Beate Symon}
May blessed Simon, with Thaddeus glorious,
Regard our weeping, and our sighs of penitence:
And, though our trespass merit endless misery,
Win us an entrance to celestial happiness.
}

\hymn{aeternaChristiMunera}{
2 The Church in these her princes boasts,
These victor chiefs of warrior hosts:
The soldiers of the heavenly hall,
The lights that rose on earth for all.

3 ’Twas thus the yearning faith of Saints,
Th’ unconquer’d hope that never faints,
The love of Christ that knows not shame,
The Prince of this world overcame.

4 In these the Father’s glory shone;
In these the will of God the Son;
In these exults the Holy Ghost;
Through these rejoice the Heavenly host.

5 Redeemer, hear us of thy Love,
That, with the glorious band above,
Hereafter, of thine endless grace,
Thy servants also may have place.  Amen.
}

\V Thou hast given an heritage.  \R Unto those that fear thy Name, O Lord.


\hymn{exultetCelumLaudibus}{
2 O ye who, throned in glory dread,
Shall judge the living and the dead—
True lights, the world illumining,
Regard the suppliant prayer we bring.

3 The gates of heav’n, at your command,
To all or closed or open stand:
May we, at your august decree,
Be loosed from our iniquity.

4 The power, of old to you convey’d,
Sickness and health alike obeyed:
May ye our ailing souls once more
To strength and holiness restore.

5 That Christ, th’ avenging Judge of doom,
When he at time’s last end shall come,
May grant us, for his mercy’s sake,
Of joys eternal to partake.

<{Ordinary Doxology:}>
6 All laud to God the Father be,
All praise, eternal Son, to thee,
All glory, as is ever meet,
To God the holy Paraclete. Amen.
}

\V They declared the works of God.  \R And wisely considered of his doings.

\section{One or More Apostles or an Evangelist in Paschal-Tide}
TODO

\section{Of one Martyr}
TODO

\section{Of Many Martyrs}
TODO

\section{Of a Confessor}
TODO


\section{Of a Virgin}

Evensong and Mattins
(Proper evensong tune is as a confessor, iste confessor)
¶ Note that if the Virgin be not a Martyr, verses 2 and 3 are ommitted.
¶ For Many Virgins, the hymn and \V is {Ihesu, corona virginum}, as at Lauds.
¶ For a Matron, begin at verse 4.

\hymn{virginisProles}{
*2 She, thine own maiden, double blessing winneth,
Striving to vanquish all her nature’s weakness.
E’en by that weakness o’er a world of bloodshed
Victory gaining.

*3 Death and its terrors undismay’d beholding,
Death’s cruel handmaid, torture, she despiseth;
Shedding her life-blood, meet is she to enter
Holiest heaven.

4 God ever-loving, as for us she pleadeth,
Pity our failings, all our sins forgiving:
Thus shall re-echo pure and heart-felt praises
Unto thine honour.

5 Praise to the Father, to the Sole-begotten,
And the blest Spirit, with the twain co-equal,
One only Godhead, who throughout the ages
Reigneth for ever. Amen.
}

{Evensong.} \V Full of grace are thy líps. \R Therefore God hath blessed thee for éver. (Allelúya).

{Mattins.} \V God shall give her the help of his cóuntenance.  \R God is in the midst of her, therefore shall she not be remóved. (Allelúya).


¶ For Many Virgins, the hymn and \V is {Rex gloriose martyrum}, as at Lauds for Many Martyrs.
¶ This tune is for 2nd Evensong; At Mattins it is sung to {Veni, redemptor Gentium}.  During Christmas tide, at both hours, to Christe Redemptor Omnium, and during eastertide to Aurora Lucit - apostles

\hymn{jesuCoronaVirginum}{
2 Among the lilies thou dost feed,
By Virgin quires accompanied—
With glory deck’d, the spotless brides
Whose bridal gifts thy love provides.

3 They, wheresoe’er thy footsteps bend,
With hymns and praises still attend:
In blessed troops they follow thee,
With dance, and song, and melody.

4. We pray thee therefore to bestow
Upon our senses here below
Thy grace, that so we may endure
From taint of all corruption pure.

Ordinary Doxology:
5 All laud to God the Father be,
All praise, eternal Son, to thee:
All glory, as is ever meet,
To God the holy Paraclete. Amen.
}

\V The virgins that be her fellows shall bear her company.  \R And shall be brought unto thee.  (Alleluya).

Sequence
Virgines egregie

Virgin Saints of high renown,
Virgins consecrated,
Ye before your Spouse appear
Crown’d and decorated:
With the everlasting rest
Ye on high are gifted;
Let a new-made song of praise
To your Lord be lifted.

Chastity’s own lily sweet
Ye were well deserving,
For the love of God’s dear Son,
Which ye were preserving:
Ye, to be the Spirit’s shrine,
As your lot were choosing,
Earthly love and wedlock’s bonds
Constantly refusing.

Flowers of holy modest
Were your chiefest treasure;
So ye trod beneath your feet
Every fleshly pleasure:
Thus the prize of purity
Hath to you been meted;
With the Virgin’s stainless Son
Ye for aye are seated.


\chapter{Proper of Saints}
November 30
S.\ Andrew, Ap. M.

December 6
S.\ Nicholas, Bp. C.

December 8
Conception of the B.\ V. Mary

December 13
S.\ Lucy, V.\ M.

December 21
S.\ Thomas, Ap.\ M.

January 18
S.\ Prisca, V.\ M.

January 20
SS.\ Fabian \& Sebastian, MM.

January 21
S.\ Agnes, V.\ M.\

January 22
S.\ Vincent, D.\ M.

January 25
Conversion of S.\ Paul

February 2
Purification of the B.\ V.\ Mary

February 3
S.\ Blaise, Bp.\ M.

February 5
S.\ Agatha, V.\ M.

Feburary 14
S.\ Valentine, Bp.\ M.

February 24 (In Leap-Year Feb. 25)
S.\ Matthias, Ap.\ M.

March 1
S.\ David, Bp.\ C.

March 2
S.\ David, Bp.\ C.

..

TODO

..

May 3
Invention of the Holy Cross

...

TODO

...

June 24
Nativity of S.\ John the Baptist

...

TODO

...

June 29
SS.\ Peter \& Paul, App.\ MM.


July 2
Visitation of the B.\ V.\ Mary

...

TODO

...

July 22
S.\ Mary Magdalen

July 25
S.\ James, Ap.\ M.

July 26
S.\ Anna, Mother of the B.\ V.\ Mary


August 1
S. Peter's Chains
As for the Common of apostles

August 6
\section{Transfiguration of our Lord}
\hymn{celestisFormamGlorie}{
2 Tale for all ages to declare;
For with the three disciples there,
Where Moses and Elias meet,
The Lord holds converse high and sweet.

3 The chosen witnesses stand nigh,
Of Grace, the Law, and Prophecy:
And from the cloud the Holy One
Bears record to the Only Son.

4 With face more bright than noon-tide ray,
Christ deigns to manifest to-day
What glory shall be theirs above,
Who joy in God with perfect love.

5 And faithful hearts are raised on high
By this great vision’s mystery;
For which in yearly course we raise
The voice of prayer, the hymn of praise.

6 Thou Father,—thou, eternal Son,
Thou, holy Spirit, Three in One,
To this same glory bring us nigh,
That we may see thee eye to eye. Amen.
}

\V Let us worship the Father and the Son, with the Holy Spirit.  \R Reigning in his majesty.


\hymn{oSatorRerum}{
2 While the night fleeteth, we our votive anthems
Frame to thine honour; grant that they may please thee;
And as we hymn thee, Source of Light eternal,
    Ever refresh us.

3 Sunlike thy visage shone with rays of splendour,
Brightly thy raiment gleam’d with snowy whiteness,
When mid the Prophets, Moses and Elias,
    Thou wast transfigured.

4 Then did the Father own thee Sole-begotten;
Thou art the glory of the holy Angels;
Thee, the Way, Virtue, Life, the world’s Salvation,
    Ever confess we.

5 Glory and power be to thee, Creator,
Who alone all things rulest and controllest,
Throned in thy kingdom, Monarch everlasting,
    Trinal and Onely. Amen.
}

\V Let us worship the Father and the Son, with the Holy Spirit.  \R Reigning in his majesty.

\hymn{oNataLuxDeLumine}{
2 Thou who, for lost transgressors’ sake,
Didst not disdain our flesh to take,
O grant that living members we
Of that thy Body blest may be.

3 Beyond the sun thine aspect bright;
Thy raiment as the snowdrift white:
To chosen witnesses made known,
Thy Godhead on the mount was shown.

4 Seers, from their children’s eyes conceal’d,
To thy disciples stood reveal’d;
On each thou didst thy power bestow
Thee as eternal God to know.

5 The Father, from his heav’nly throne,
Proclaim’d thee his Anointed Son,
And we with faithful hearts no less,
Thee, King of glory, aye confess.

6 May we thy splendour day by day
In innocence of life display;
And thus to joys beyond the skies
In holy converse heav’nward rise.

7 Eternal God, of kings the King,
To thee our hymns of praise we bring;
Who, Threefold Deity, alone
Dost reign to endless ages One. Amen.
}

\V Blessed be the Name of the Lord.  \R From this time forth for evermore.



August 7
\section{The most sweet Name of Jesus}

\hymn{exultetCorPrecordiis}{
2 ‘Jesus’ the comfortless consoles,
‘Jesus’ each sinful fever quells,
‘Jesus’ the hosts of hell controls,
‘Jesus’ each deadly foe repels.

3 ‘Jesus!’ how sweetly doth it sound
In every measure, prose, or psalm:
It makes each quick’ning bosom bound,
And soothes us with divinest calm.

4 Far let that Name exalted ring;
On every tongue let ‘Jesus’ be:
Let heart and voice together sing
The Name that cures each malady.

5 Jesu, the sinner’s health, abide
With us, and hearken to our prayer;
The frail and erring wanderer guide,
The penitent transgressor spare.

6 Be thy dear Name our sure defence,
In every peril be our stay;
And, purging us from sin’s offence,
Perfect us in the better way.

7 O Christ, all glory be to thee,
Resplendent with this Name divine;
All Honour, worship, majesty,
Dear Lord, for evermore be thine.

8 O Jesu, born of spotless Maid,
To thee all praise and glory be:
Like glory to the Sire be paid,
And holy Ghost eternally. Amen.
}
\V All the world shall worship thee, O God, and sing of thee.  \R And shall praise thy Name, O Lord.


¶ At Compline
[[Sequence]] Alma chorus Domini, {as above on} Whitsun.


\hymn{jesuDulcisMemoria}{
2 No word is sung more sweet than this;
No name is heard more full of bliss;
No thought brings sweeter comfort nigh,
Than Jesus, Son of God most high.

3 Jesu! the hope of souls forlorn!
How good to them for sin that mourn!
To them that seek thee, O how kind!
But what art thou to them that find?

4 Jesu, thou sweetness pure and blest,
Life’s Fountain, Light of souls distressed;
Surpassing all that heart requires,
Exceeding all that soul desires.

5 No tongue of mortals can express,
No letters write its blessedness:
Alone who hath thee in his heart
Knows, love of Jesus, what thou art.

6 O Jesu, King of wondrous might!
O Victor, glorious from the fight!
Sweetness that may not be express’d,
And altogether loveliest.

7 Remain with us, O Lord, to-day;
In every heart thy grace display:
That, now the shades of night are fled,
On thee our spirits may be fed.

8 All honour, laud, and glory be,
O Jesu, Virgin-born, to thee:
All glory, as is ever meet,
To Father and to Paraclete. Amen.
}
\V Our help is in the Name of the Lord.  \R Who hath made heaven and earth.


\hymn{jesuAuctorClemencie}{
2 O Jesu, Pride of Angel-host,
O Song, the ear that charmeth most,
To lips as honey, wondrous fine,
To heart as nectar, all-divine.

3 O Jesu, Flower of Mother-Maid,
As honey-comb to man display’d:
The glory of the world below,
Thy light’s true light on us bestow.

4 Than sun-ray more serenely calm,
More fragrant than the breath of balm
Sweeter than sweetness’ self can be,
And lovel{i}er than all else to see.

5 Jesu, who highest bounty art,
And wondrous joyaunce of the heart,
Of goodness the infinity,
Knit us in bond of love to thee.

6 O King of virtues, King renown’d,
With glory and with victory crown’d!
Jesu, who dost all grace supply,
The worship of the courts on high.

7 The Quires above thy praise proclaim,
And echo all thy matchless fame:
Jesus on joyful earth hath smiled,
And us to God hath reconciled.

8 All honour, laud, and glory be,
O Jesu, Virgin-born, to thee:
All glory, as is ever meet,
To Father and to Paraclete. Amen.
}
\V Blessed be the Name of the Lord.  \R From this time forth for evermore.



238 Jesu the ver thought is sweet! (The Rosy Sequency)
TODO

August 10
S.\ Laurence, D.\ M.

August 15
Assumption of the B.\ V.\ Mary


...

TODO
...

September 29
S.\ Michael and All Angels

...

TODO

...

November 1
All Saints


\chapter{Hymns for the Lesser Hours}
\section{At Prime}
\section{At Tierce}
\section{At Sext}
\section{At None}
\section{At Compline}





\end{document}
